---
title: "Filter_Tweets"
author: "Adam Chapnik"
date: "12/1/2020"
output: html_document
---
```{r}
library(rtweet)
library(tidytext)
library(ggpubr)
library(tidyverse)
library(dplyr)
library(glue)
library(googleLanguageR)
library(rvest)
usethis::edit_r_environ()
gl_auth("[GL_AUTH].json")
```

```{r}
## Keep rtweet updated ##
## install devtools package if it's not already
if (!requireNamespace("devtools", quietly = TRUE)) {
  install.packages("devtools")
}

## install dev version of rtweet from github
devtools::install_github("mkearney/rtweet")

## load rtweet package
library(rtweet)

tw_token <-
rtweet::create_token(
consumer_key = "[consumer_key]",
consumer_secret = "[consumer_secret]",
access_token = "[access_token]",
access_secret = "[access_secret]"
)
```

```{r eval=FALSE, include=FALSE}
df <- read_csv("Tweets.csv")
chinese_en <- read_csv("Translated_tweets.csv")
english <- df %>% dplyr::filter(lang == "en")
```

Now that I have a full dataset of tweets from the main Chinese accounts during the period of interest, in English or Chinese, I can filter for the tweets with keywords and hashtags I'm interested in.

I will filter for keywords in the tweets themselves for the English dataset and the translated Chinese dataset. For the tweets in which no keywords were found, I will then filter for hashtags. I would filter for text found in attached images and websites, but the R OCR package Tesseract is not able to distinguish text well enough for that purpose. Obviously, filtering for keywords like this will also fail to include typos or will include tweets that are actually not of interest, but that excess in/exclusion should be negligible

The keywords are under three umbrellas: US, HK, and BLM. I will filter by tweets that have: (US and HK) or (US and BLM) or (HK and BLM) or BLM. Under each umbrella, for the tweets written in English, the specific keywords (i.e. strings of letters) are:

US: US, U.S., America, United States, Washington
HK: Hong Kong, HKSAR
BLM: Black Lives, BLM, black lives, racism, George Floyd

For the tweets written in Chinese and translated to English, the specific keywords (i.e. strings of letters) are:

US: US, U.S., America, United States, Washington
HK: Hong Kong, HKSAR
BLM: racism, George Floyd

```{r}
## filter for keywords (english)
x <- list(c("US", "U.S.", "America", "United States", "Washington"), c("Hong Kong", "HKSAR"), c("Black Lives", "BLM", "black lives", "racism", "George Floyd"))
# (US and HK)
a <- dplyr::filter(english, (grepl(x[[1]][1], text) & grepl(x[[2]][1], text)))
b <- anti_join(english, a) %>% 
    dplyr::filter((grepl(x[[1]][1], text) & grepl(x[[2]][2], text)))
c <- anti_join(english, b) %>% 
    dplyr::filter((grepl(x[[1]][2], text) & grepl(x[[2]][1], text)))
d <- anti_join(english, c) %>% 
    dplyr::filter((grepl(x[[1]][2], text) & grepl(x[[2]][2], text)))
e <- anti_join(english, d) %>% 
    dplyr::filter((grepl(x[[1]][3], text) & grepl(x[[2]][1], text)))
f <- anti_join(english, e) %>% 
    dplyr::filter((grepl(x[[1]][3], text) & grepl(x[[2]][2], text)))
g <- anti_join(english, f) %>% 
    dplyr::filter((grepl(x[[1]][4], text) & grepl(x[[2]][1], text)))
h <- anti_join(english, g) %>% 
    dplyr::filter((grepl(x[[1]][4], text) & grepl(x[[2]][2], text)))
i <- anti_join(english, h) %>% 
    dplyr::filter((grepl(x[[1]][5], text) & grepl(x[[2]][1], text)))
j <- anti_join(english, i) %>% 
    dplyr::filter((grepl(x[[1]][5], text) & grepl(x[[2]][2], text)))
filtered_english1 <- rbind(a,b,c,d,e,f,g,h,i,j)
# (HK and BLM)
a <- dplyr::filter(english, (grepl(x[[3]][1], text) & grepl(x[[2]][1], text)))
b <- anti_join(english, a) %>% 
    dplyr::filter((grepl(x[[3]][1], text) & grepl(x[[2]][2], text)))
c <- anti_join(english, b) %>% 
    dplyr::filter((grepl(x[[3]][2], text) & grepl(x[[2]][1], text)))
d <- anti_join(english, c) %>% 
    dplyr::filter((grepl(x[[3]][2], text) & grepl(x[[2]][2], text)))
e <- anti_join(english, d) %>% 
    dplyr::filter((grepl(x[[3]][3], text) & grepl(x[[2]][1], text)))
f <- anti_join(english, e) %>% 
    dplyr::filter((grepl(x[[3]][3], text) & grepl(x[[2]][2], text)))
g <- anti_join(english, f) %>% 
    dplyr::filter((grepl(x[[3]][4], text) & grepl(x[[2]][1], text)))
h <- anti_join(english, g) %>% 
    dplyr::filter((grepl(x[[3]][4], text) & grepl(x[[2]][2], text)))
i <- anti_join(english, h) %>% 
    dplyr::filter((grepl(x[[3]][5], text) & grepl(x[[2]][1], text)))
j <- anti_join(english, i) %>% 
    dplyr::filter((grepl(x[[3]][5], text) & grepl(x[[2]][2], text)))
filtered_english2 <- rbind(a,b,c,d,e,f,g,h,i,j)
# (US and BLM)
a <- dplyr::filter(english, (grepl(x[[1]][1], text) & grepl(x[[3]][1], text)))
b <- anti_join(english, a) %>% 
    dplyr::filter((grepl(x[[1]][1], text) & grepl(x[[3]][2], text)))
c <- anti_join(english, b) %>% 
    dplyr::filter((grepl(x[[1]][1], text) & grepl(x[[3]][3], text)))
d <- anti_join(english, c) %>% 
    dplyr::filter((grepl(x[[1]][1], text) & grepl(x[[3]][4], text)))
e <- anti_join(english, d) %>% 
    dplyr::filter((grepl(x[[1]][1], text) & grepl(x[[3]][5], text)))
f <- anti_join(english, e) %>% 
    dplyr::filter((grepl(x[[1]][2], text) & grepl(x[[3]][1], text)))
g <- anti_join(english, f) %>% 
   dplyr::filter((grepl(x[[1]][2], text) & grepl(x[[3]][2], text)))
h <- anti_join(english, g) %>% 
    dplyr::filter((grepl(x[[1]][2], text) & grepl(x[[3]][3], text)))
i <- anti_join(english, h) %>% 
    dplyr::filter((grepl(x[[1]][2], text) & grepl(x[[3]][4], text)))
j <- anti_join(english, i) %>% 
    dplyr::filter((grepl(x[[1]][2], text) & grepl(x[[3]][5], text)))
k <- anti_join(english, j) %>% 
    dplyr::filter((grepl(x[[1]][3], text) & grepl(x[[3]][1], text)))
l <- anti_join(english, k) %>% 
    dplyr::filter((grepl(x[[1]][3], text) & grepl(x[[3]][2], text)))
m <- anti_join(english, l) %>%
    dplyr::filter((grepl(x[[1]][3], text) & grepl(x[[3]][3], text)))
n <- anti_join(english, m) %>% 
    dplyr::filter((grepl(x[[1]][3], text) & grepl(x[[3]][4], text)))
o <- anti_join(english, n) %>% 
    dplyr::filter((grepl(x[[1]][3], text) & grepl(x[[3]][5], text)))
p <- anti_join(english, o) %>% 
    dplyr::filter((grepl(x[[1]][4], text) & grepl(x[[3]][1], text)))
q <- anti_join(english, p) %>% 
    dplyr::filter((grepl(x[[1]][4], text) & grepl(x[[3]][2], text)))
r <- anti_join(english, q) %>% 
    dplyr::filter((grepl(x[[1]][4], text) & grepl(x[[3]][3], text)))
s <- anti_join(english, r) %>% 
    dplyr::filter((grepl(x[[1]][4], text) & grepl(x[[3]][4], text)))
t <- anti_join(english, s) %>% 
    dplyr::filter((grepl(x[[1]][4], text) & grepl(x[[3]][5], text)))
u <- anti_join(english, t) %>% 
    dplyr::filter((grepl(x[[1]][5], text) & grepl(x[[3]][1], text)))
v <- anti_join(english, u) %>% 
    dplyr::filter((grepl(x[[1]][5], text) & grepl(x[[3]][2], text)))
w <- anti_join(english, v) %>% 
    dplyr::filter((grepl(x[[1]][5], text) & grepl(x[[3]][3], text)))
y <- anti_join(english, w) %>% 
    dplyr::filter((grepl(x[[1]][5], text) & grepl(x[[3]][4], text)))
z <- anti_join(english, y) %>% 
    dplyr::filter((grepl(x[[1]][5], text) & grepl(x[[3]][5], text)))
filtered_english3 <- rbind(a,b,c,d,e,f,g,h,i,j,k,l,m,n,o,p,q,r,s,t,u,v,w,y,z)
# BLM
a <- dplyr::filter(english, (grepl(x[[3]][1], text)))
b <- anti_join(english, a) %>% 
    dplyr::filter((grepl(x[[3]][2], text)))
c <- anti_join(english, b) %>% 
    dplyr::filter((grepl(x[[3]][3], text)))
d <- anti_join(english, c) %>% 
    dplyr::filter((grepl(x[[3]][4], text)))
e <- anti_join(english, d) %>% 
    dplyr::filter((grepl(x[[3]][5], text)))
filtered_english4 <- rbind(a,b,c,d,e)
filtered_english <- rbind(filtered_english1, filtered_english2, filtered_english3, filtered_english4)

## filter for keywords (chinese)
x <- list(c("US", "U.S.", "America", "United States", "Washington"), c("Hong Kong", "HKSAR"), c("racism", "George Floyd"))
# (US and HK)
a <- dplyr::filter(chinese_en, (grepl(x[[1]][1], text_en) & grepl(x[[2]][1], text_en)))
b <- anti_join(chinese_en, a) %>% 
    dplyr::filter((grepl(x[[1]][1], text_en) & grepl(x[[2]][2], text_en)))
c <- anti_join(chinese_en, b) %>% 
    dplyr::filter((grepl(x[[1]][2], text_en) & grepl(x[[2]][1], text_en)))
d <- anti_join(chinese_en, c) %>% 
    dplyr::filter((grepl(x[[1]][2], text_en) & grepl(x[[2]][2], text_en)))
e <- anti_join(chinese_en, d) %>% 
    dplyr::filter((grepl(x[[1]][3], text_en) & grepl(x[[2]][1], text_en)))
f <- anti_join(chinese_en, e) %>% 
    dplyr::filter((grepl(x[[1]][3], text_en) & grepl(x[[2]][2], text_en)))
g <- anti_join(chinese_en, f) %>% 
    dplyr::filter((grepl(x[[1]][4], text_en) & grepl(x[[2]][1], text_en)))
h <- anti_join(chinese_en, g) %>% 
    dplyr::filter((grepl(x[[1]][4], text_en) & grepl(x[[2]][2], text_en)))
i <- anti_join(chinese_en, h) %>% 
    dplyr::filter((grepl(x[[1]][5], text_en) & grepl(x[[2]][1], text_en)))
j <- anti_join(chinese_en, i) %>% 
    dplyr::filter((grepl(x[[1]][5], text_en) & grepl(x[[2]][2], text_en)))
filtered_chinese1 <- rbind(a,b,c,d,e,f,g,h,i,j)
# (HK and BLM)
a <- dplyr::filter(chinese_en, (grepl(x[[3]][1], text_en) & grepl(x[[2]][1], text_en)))
b <- anti_join(chinese_en, a) %>% 
    dplyr::filter((grepl(x[[3]][1], text_en) & grepl(x[[2]][2], text_en)))
c <- anti_join(chinese_en, b) %>% 
    dplyr::filter((grepl(x[[3]][2], text_en) & grepl(x[[2]][1], text_en)))
d <- anti_join(chinese_en, c) %>% 
    dplyr::filter((grepl(x[[3]][2], text_en) & grepl(x[[2]][2], text_en)))
filtered_chinese2 <- rbind(a,b,c,d)
# (US and BLM)
a <- dplyr::filter(chinese_en, (grepl(x[[1]][1], text_en) & grepl(x[[3]][1], text_en)))
b <- anti_join(chinese_en, a) %>% 
    dplyr::filter((grepl(x[[1]][1], text_en) & grepl(x[[3]][2], text_en)))
c <- anti_join(chinese_en, b) %>% 
    dplyr::filter((grepl(x[[1]][2], text_en) & grepl(x[[3]][1], text_en)))
d <- anti_join(chinese_en, c) %>% 
    dplyr::filter((grepl(x[[1]][2], text_en) & grepl(x[[3]][2], text_en)))
e <- anti_join(chinese_en, d) %>% 
    dplyr::filter((grepl(x[[1]][3], text_en) & grepl(x[[3]][1], text_en)))
f <- anti_join(chinese_en, e) %>% 
    dplyr::filter((grepl(x[[1]][3], text_en) & grepl(x[[3]][2], text_en)))
g <- anti_join(chinese_en, f) %>% 
    dplyr::filter((grepl(x[[1]][4], text_en) & grepl(x[[3]][1], text_en)))
h <- anti_join(chinese_en, g) %>% 
    dplyr::filter((grepl(x[[1]][4], text_en) & grepl(x[[3]][2], text_en)))
i <- anti_join(chinese_en, h) %>% 
    dplyr::filter((grepl(x[[1]][5], text_en) & grepl(x[[3]][1], text_en)))
j <- anti_join(chinese_en, i) %>% 
    dplyr::filter((grepl(x[[1]][5], text_en) & grepl(x[[3]][2], text_en)))
filtered_chinese3 <- rbind(a,b,c,d,e,f,g,h,i,j)
# BLM
a <- dplyr::filter(chinese_en, (grepl(x[[3]][1], text_en)))
b <- anti_join(chinese_en, a) %>% 
    dplyr::filter((grepl(x[[3]][2], text_en)))
filtered_chinese4 <- rbind(a,b)
filtered_chinese <- rbind(filtered_chinese1, filtered_chinese2, filtered_chinese3, filtered_chinese4)
```

Now, excluding the tweets filtered so far, I will filter by tweets that have: (US and BLM) or (HK and BLM) or (US and Other) or (HK and Other) or (BLM and Other) or BLM. Under each umbrella, for the tweets written in English, the specific hashtags (i.e. strings of letters) are:

BLM: BlackLivesMatter, BLM, racism, Racism, George, ICantBreathe, Floyd
HK: HK, HongKong, hk
US: US, America, UnitedStates, Washington 
Other: DoubleStandard, doublestandard

Under each umbrella, for the tweets written in Chinese and translated to English, the specific hashtags (i.e. strings of letters) are:

BLM: BlackLivesMatter, George, Floyd
HK: HK, HongKong
US: US, America, UnitedStates, Washington 

```{r}
## filter for hashtags (english)
x <- list(c("US", "America", "UnitedStates", "Washington"), c("HongKong", "HK", "hk"), c("racism", "George", "BlackLivesMatter", "BLM", "Racism", "Floyd", "ICantBreathe"), c("DoubleStandard", "doublestandard"))
start <- anti_join(english, filtered_english)
# (US and BLM)
a <- start %>% filter((grepl(x[[1]][1], hashtags) & grepl(x[[3]][1], hashtags)))
b <- anti_join(start, a) %>% filter((grepl(x[[1]][1], hashtags) & grepl(x[[3]][2], hashtags)))
c <- anti_join(start, b) %>% filter((grepl(x[[1]][1], hashtags) & grepl(x[[3]][3], hashtags)))
d <- anti_join(start, c) %>% filter((grepl(x[[1]][1], hashtags) & grepl(x[[3]][4], hashtags)))
e <- anti_join(start, d) %>% filter((grepl(x[[1]][1], hashtags) & grepl(x[[3]][5], hashtags)))
f <- anti_join(start, e) %>% filter((grepl(x[[1]][1], hashtags) & grepl(x[[3]][6], hashtags)))
g <- anti_join(start, f) %>% filter((grepl(x[[1]][1], hashtags) & grepl(x[[3]][7], hashtags)))
h <- anti_join(start, g) %>% filter((grepl(x[[1]][2], hashtags) & grepl(x[[3]][1], hashtags)))
i <- anti_join(start, h) %>% filter((grepl(x[[1]][2], hashtags) & grepl(x[[3]][2], hashtags)))
j <- anti_join(start, i) %>% filter((grepl(x[[1]][2], hashtags) & grepl(x[[3]][3], hashtags)))
k <- anti_join(start, j) %>% filter((grepl(x[[1]][2], hashtags) & grepl(x[[3]][4], hashtags)))
l <- anti_join(start, k) %>% filter((grepl(x[[1]][2], hashtags) & grepl(x[[3]][5], hashtags)))
m <- anti_join(start, l) %>% filter((grepl(x[[1]][2], hashtags) & grepl(x[[3]][6], hashtags)))
n <- anti_join(start, m) %>% filter((grepl(x[[1]][2], hashtags) & grepl(x[[3]][7], hashtags)))
o <- anti_join(start, n) %>% filter((grepl(x[[1]][3], hashtags) & grepl(x[[3]][1], hashtags)))
p <- anti_join(start, o) %>% filter((grepl(x[[1]][3], hashtags) & grepl(x[[3]][2], hashtags)))
q <- anti_join(start, p) %>% filter((grepl(x[[1]][3], hashtags) & grepl(x[[3]][3], hashtags)))
r <- anti_join(start, q) %>% filter((grepl(x[[1]][3], hashtags) & grepl(x[[3]][4], hashtags)))
s <- anti_join(start, r) %>% filter((grepl(x[[1]][3], hashtags) & grepl(x[[3]][5], hashtags)))
t <- anti_join(start, s) %>% filter((grepl(x[[1]][3], hashtags) & grepl(x[[3]][6], hashtags)))
u <- anti_join(start, t) %>% filter((grepl(x[[1]][3], hashtags) & grepl(x[[3]][7], hashtags)))
v <- anti_join(start, u) %>% filter((grepl(x[[1]][4], hashtags) & grepl(x[[3]][1], hashtags)))
w <- anti_join(start, v) %>% filter((grepl(x[[1]][4], hashtags) & grepl(x[[3]][2], hashtags)))
y <- anti_join(start, w) %>% filter((grepl(x[[1]][4], hashtags) & grepl(x[[3]][3], hashtags)))
z <- anti_join(start, y) %>% filter((grepl(x[[1]][4], hashtags) & grepl(x[[3]][4], hashtags)))
aa <- anti_join(start, z) %>% filter((grepl(x[[1]][4], hashtags) & grepl(x[[3]][5], hashtags)))
bb <- anti_join(start, aa) %>% filter((grepl(x[[1]][4], hashtags) & grepl(x[[3]][6], hashtags)))
cc <- anti_join(start, bb) %>% filter((grepl(x[[1]][4], hashtags) & grepl(x[[3]][7], hashtags)))
filtered_english1 <- rbind(a,b,c,d,e,f,g,h,i,j,k,l,m,n,o,p,q,r,s,t,u,v,w,y,z,aa,bb,cc)
# (HK and BLM)
a <- start %>% filter((grepl(x[[2]][1], hashtags) & grepl(x[[3]][1], hashtags)))
b <- anti_join(start, a) %>% filter((grepl(x[[2]][1], hashtags) & grepl(x[[3]][2], hashtags)))
c <- anti_join(start, b) %>% filter((grepl(x[[2]][1], hashtags) & grepl(x[[3]][3], hashtags)))
d <- anti_join(start, c) %>% filter((grepl(x[[2]][1], hashtags) & grepl(x[[3]][4], hashtags)))
e <- anti_join(start, d) %>% filter((grepl(x[[2]][1], hashtags) & grepl(x[[3]][5], hashtags)))
f <- anti_join(start, e) %>% filter((grepl(x[[2]][1], hashtags) & grepl(x[[3]][6], hashtags)))
g <- anti_join(start, f) %>% filter((grepl(x[[2]][1], hashtags) & grepl(x[[3]][7], hashtags)))
h <- anti_join(start, g) %>% filter((grepl(x[[2]][2], hashtags) & grepl(x[[3]][1], hashtags)))
i <- anti_join(start, h) %>% filter((grepl(x[[2]][2], hashtags) & grepl(x[[3]][2], hashtags)))
j <- anti_join(start, i) %>% filter((grepl(x[[2]][2], hashtags) & grepl(x[[3]][3], hashtags)))
k <- anti_join(start, j) %>% filter((grepl(x[[2]][2], hashtags) & grepl(x[[3]][4], hashtags)))
l <- anti_join(start, k) %>% filter((grepl(x[[2]][2], hashtags) & grepl(x[[3]][5], hashtags)))
m <- anti_join(start, l) %>% filter((grepl(x[[2]][2], hashtags) & grepl(x[[3]][6], hashtags)))
n <- anti_join(start, m) %>% filter((grepl(x[[2]][2], hashtags) & grepl(x[[3]][7], hashtags)))
o <- anti_join(start, n) %>% filter((grepl(x[[2]][3], hashtags) & grepl(x[[3]][1], hashtags)))
p <- anti_join(start, o) %>% filter((grepl(x[[2]][3], hashtags) & grepl(x[[3]][2], hashtags)))
q <- anti_join(start, p) %>% filter((grepl(x[[2]][3], hashtags) & grepl(x[[3]][3], hashtags)))
r <- anti_join(start, q) %>% filter((grepl(x[[2]][3], hashtags) & grepl(x[[3]][4], hashtags)))
s <- anti_join(start, r) %>% filter((grepl(x[[2]][3], hashtags) & grepl(x[[3]][5], hashtags)))
t <- anti_join(start, s) %>% filter((grepl(x[[2]][3], hashtags) & grepl(x[[3]][6], hashtags)))
u <- anti_join(start, t) %>% filter((grepl(x[[2]][3], hashtags) & grepl(x[[3]][7], hashtags)))
filtered_english2 <- rbind(a,b,c,d,e,f,g,h,i,j,k,l,m,n,o,p,q,r,s,t,u)
# (US and Other)
a <- start %>% filter((grepl(x[[1]][1], hashtags) & grepl(x[[4]][1], hashtags)))
b <- anti_join(start, a) %>% filter((grepl(x[[1]][1], hashtags) & grepl(x[[4]][2], hashtags)))
c <- anti_join(start, b) %>% filter((grepl(x[[1]][2], hashtags) & grepl(x[[4]][1], hashtags)))
d <- anti_join(start, c) %>% filter((grepl(x[[1]][2], hashtags) & grepl(x[[4]][2], hashtags)))
e <- anti_join(start, d) %>% filter((grepl(x[[1]][3], hashtags) & grepl(x[[4]][1], hashtags)))
f <- anti_join(start, e) %>% filter((grepl(x[[1]][3], hashtags) & grepl(x[[4]][2], hashtags)))
g <- anti_join(start, f) %>% filter((grepl(x[[1]][4], hashtags) & grepl(x[[4]][1], hashtags)))
h <- anti_join(start, g) %>% filter((grepl(x[[1]][4], hashtags) & grepl(x[[4]][2], hashtags)))
filtered_english3 <- rbind(a,b,c,d,e,f,g,h)
# (HK and Other)
a <- start %>% filter((grepl(x[[2]][1], hashtags) & grepl(x[[4]][1], hashtags)))
b <- anti_join(start, a) %>% filter((grepl(x[[2]][1], hashtags) & grepl(x[[4]][2], hashtags)))
c <- anti_join(start, b) %>% filter((grepl(x[[2]][2], hashtags) & grepl(x[[4]][1], hashtags)))
d <- anti_join(start, c) %>% filter((grepl(x[[2]][2], hashtags) & grepl(x[[4]][2], hashtags)))
e <- anti_join(start, d) %>% filter((grepl(x[[2]][3], hashtags) & grepl(x[[4]][1], hashtags)))
f <- anti_join(start, e) %>% filter((grepl(x[[2]][3], hashtags) & grepl(x[[4]][2], hashtags)))
filtered_english4 <- rbind(a,b,c,d,e,f)
# (BLM and Other)
a <- start %>% filter((grepl(x[[1]][1], hashtags) & grepl(x[[4]][1], hashtags)))
b <- anti_join(start, a) %>% filter((grepl(x[[1]][1], hashtags) & grepl(x[[4]][2], hashtags)))
c <- anti_join(start, b) %>% filter((grepl(x[[1]][2], hashtags) & grepl(x[[4]][1], hashtags)))
d <- anti_join(start, c) %>% filter((grepl(x[[1]][2], hashtags) & grepl(x[[4]][2], hashtags)))
e <- anti_join(start, d) %>% filter((grepl(x[[1]][3], hashtags) & grepl(x[[4]][1], hashtags)))
f <- anti_join(start, e) %>% filter((grepl(x[[1]][3], hashtags) & grepl(x[[4]][2], hashtags)))
g <- anti_join(start, f) %>% filter((grepl(x[[1]][4], hashtags) & grepl(x[[4]][1], hashtags)))
h <- anti_join(start, g) %>% filter((grepl(x[[1]][4], hashtags) & grepl(x[[4]][2], hashtags)))
i <- anti_join(start, h) %>% filter((grepl(x[[1]][5], hashtags) & grepl(x[[4]][1], hashtags)))
j <- anti_join(start, i) %>% filter((grepl(x[[1]][5], hashtags) & grepl(x[[4]][2], hashtags)))
k <- anti_join(start, j) %>% filter((grepl(x[[1]][6], hashtags) & grepl(x[[4]][1], hashtags)))
l <- anti_join(start, k) %>% filter((grepl(x[[1]][6], hashtags) & grepl(x[[4]][2], hashtags)))
m <- anti_join(start, l) %>% filter((grepl(x[[1]][7], hashtags) & grepl(x[[4]][1], hashtags)))
n <- anti_join(start, m) %>% filter((grepl(x[[1]][7], hashtags) & grepl(x[[4]][2], hashtags)))
filtered_english5 <- rbind(a,b,c,d,e,f,g,h,i,j,k,l,m,n)
# BLM
a <- start %>% filter(grepl(x[[3]][1], hashtags))
b <- anti_join(start, a) %>% filter(grepl(x[[3]][2], hashtags))
c <- anti_join(start, b) %>% filter(grepl(x[[3]][3], hashtags))
d <- anti_join(start, c) %>% filter(grepl(x[[3]][4], hashtags))
e <- anti_join(start, d) %>% filter(grepl(x[[3]][5], hashtags))
f <- anti_join(start, e) %>% filter(grepl(x[[3]][6], hashtags))
g <- anti_join(start, f) %>% filter(grepl(x[[3]][7], hashtags))
filtered_english6 <- rbind(a,b,c,d,e,f,g)
filtered_english <- rbind(filtered_english, filtered_english1, filtered_english2, filtered_english3, filtered_english4, filtered_english5, filtered_english6)

## filter for hashtags (chinese)
x <- list(c("US", "America", "UnitedStates", "Washington"), c("HongKong", "HK"), c("George", "BlackLivesMatter","Floyd"))
start <- anti_join(chinese_en, filtered_chinese)
# (US and BLM)
a <- start %>% filter((grepl(x[[1]][1], hashtags_en) & grepl(x[[3]][1], hashtags_en)))
b <- anti_join(start, a) %>% filter((grepl(x[[1]][1], hashtags_en) & grepl(x[[3]][2], hashtags_en)))
c <- anti_join(start, b) %>% filter((grepl(x[[1]][1], hashtags_en) & grepl(x[[3]][3], hashtags_en)))
d <- anti_join(start, c) %>% filter((grepl(x[[1]][2], hashtags_en) & grepl(x[[3]][1], hashtags_en)))
e <- anti_join(start, d) %>% filter((grepl(x[[1]][2], hashtags_en) & grepl(x[[3]][2], hashtags_en)))
f <- anti_join(start, e) %>% filter((grepl(x[[1]][2], hashtags_en) & grepl(x[[3]][3], hashtags_en)))
g <- anti_join(start, f) %>% filter((grepl(x[[1]][3], hashtags_en) & grepl(x[[3]][1], hashtags_en)))
h <- anti_join(start, g) %>% filter((grepl(x[[1]][3], hashtags_en) & grepl(x[[3]][2], hashtags_en)))
i <- anti_join(start, h) %>% filter((grepl(x[[1]][3], hashtags_en) & grepl(x[[3]][3], hashtags_en)))
j <- anti_join(start, i) %>% filter((grepl(x[[1]][4], hashtags_en) & grepl(x[[3]][1], hashtags_en)))
k <- anti_join(start, j) %>% filter((grepl(x[[1]][4], hashtags_en) & grepl(x[[3]][2], hashtags_en)))
l <- anti_join(start, k) %>% filter((grepl(x[[1]][4], hashtags_en) & grepl(x[[3]][3], hashtags_en)))
filtered_chinese1 <- rbind(a,b,c,d,e,f,g,h,i,j,k,l)
# (HK and BLM)
a <- start %>% filter((grepl(x[[2]][1], hashtags_en) & grepl(x[[3]][1], hashtags_en)))
b <- anti_join(start, a) %>% filter((grepl(x[[2]][1], hashtags_en) & grepl(x[[3]][2], hashtags_en)))
c <- anti_join(start, b) %>% filter((grepl(x[[2]][1], hashtags_en) & grepl(x[[3]][3], hashtags_en)))
d <- anti_join(start, c) %>% filter((grepl(x[[2]][2], hashtags_en) & grepl(x[[3]][1], hashtags_en)))
e <- anti_join(start, d) %>% filter((grepl(x[[2]][2], hashtags_en) & grepl(x[[3]][2], hashtags_en)))
f <- anti_join(start, e) %>% filter((grepl(x[[2]][2], hashtags_en) & grepl(x[[3]][3], hashtags_en)))
filtered_chinese2 <- rbind(a,b,c,d,e,f)
# BLM
a <- start %>% filter(grepl(x[[3]][1], hashtags_en))
b <- anti_join(start, a) %>% filter(grepl(x[[3]][2], hashtags_en))
c <- anti_join(start, b) %>% filter(grepl(x[[3]][3], hashtags_en))
filtered_chinese3 <- rbind(a,b,c)
filtered_chinese <- rbind(filtered_chinese, filtered_chinese1, filtered_chinese2, filtered_chinese3)
```

```{r}
df <- rbind(filtered_chinese, filtered_english)
status_id <- gsub("x","",df$status_id)
df$status_id <- NULL
df <- cbind(status_id, df)
df$status_id <- as.character(df$status_id)
user_id <- gsub("x","",df$user_id)
df$user_id <- NULL
df <- cbind(user_id, df)
df$user_id <- as.character(df$user_id)

df.en <- df %>% filter(lang == "en")
df.en$text_en <- NULL
df.en2 <- df %>% filter(lang == "en") %>% dplyr::select(text) %>% rename(text_en = text)
df.en <- cbind(df.en, df.en2)
df.en$hashtags_en <- NULL
df.en2 <- df %>% filter(lang == "en") %>% dplyr::select(hashtags) %>% rename(hashtags_en = hashtags)
df.en <- cbind(df.en, df.en2)
df.zh <- df %>% filter(lang == "zh")
df <- rbind(df.en, df.zh)

write_as_csv(df, "Core_tweets.csv")
```

Once the tweets are filtered down to only the ones of interest, I will find all the user_ids/handles that retweeted those tweets.


```{r}
core <- read_csv("Core_tweets.csv")
x <- unique(core$screen_name)
x <- paste0("@",x)
x <- as.data.frame(x) %>% rename(Handle = "x")
write_as_csv(x, "Filtered_Accounts.csv")
```


